---
title: "Untitled"
output: 
  html_document: 
    highlight: espresso
    keep_md: yes
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Shiny Apps are cool

If i remember correctly, my first interaction with R dates back to 2016, when out of curiosity for this "data science" thing that everyone seemed to be getting hooked on, I recovered my Coursera password and with no hesitation I enrolled in the first course** of the Data Science Specialization by JHU.

Didn't took me very long after that to get hooked up and join "everyone else" onboard the data science hype train. 

Amongst all the R things I was discovering day by day, 
the one that had the most wow-effect on my still fresh and impressionable data-scientist mind was Shiny.

Sure, writing code in the R console while sitting on your desk wearing your favorite back hoodie and listening to some 90' rock classics IS cool. 
No one argues that.

in the dark  
filtering data frames row at the speed of sound was 

But. There was something just as cool in seeing how all these raw lifeless lines of R code could yield something pretty and stylish like these clean and interactive web pages or apps that anyone could use.

I'll admit it did took me a while to build one Shiny App myself, mainly due to a hard time in coming up with a decent meaningfull idea for a web app based that essentially, runs R code.   
And in fact I didnt, this is probably the useless Shiny App ever, but I had fun making it and learned a lot so, here it is.


## All Time Ago: a very cringy name for a just as cringy Shiny App

Allright, no point in going around the houses: my first Shiny App does one thing and one thing only: it tells you how long it has been since your last All Time Low concert. 

That's it. 

You input a date and it tells you 

So... what does this have to do with data science? 
Absolutely nothing.






## Front end: how to make a Shiny App look pretty

Let's be honest here: Shiny Apps out of the box tend to look kinda flat and colorless, with sans-serif Helvetica titles layed out on a bland white background and not much more.    


But that's understandable, as they are not really ment to be looked at as much as II used for I something.


In fact, if you really care about the web-design aspect you would probably look elsewhere for    

Since my app doesn't do much in the first place, I wanted it to at least be something I enjoy looking at.  

Shiny does allow you to change the apperance of your UI, although that does require you to know some HTML and CSS or be willing to learn that.

With Shiny, the front-end (or UI) is largely (if not entirely) based upon Bootstrap, a very popular framework for building responsive website layouts without needing to loose your mind learning CSS yourself.  

That said, Bootstrap can make your life hard when trying to apply your own style on top of its default classes. 




For the calendar/date picker I did try/considered a few options: the default one from the Shiny dateInput() function comes with very few options to change its appearance, and even when I tryed playing around adding extra CSS (on top of the build-in Bootstrap classes it comes with)  the result was sub-optimal  

turned out to be difficult to style it as I wished, especially the poup I also couldn't find a way to get rid of the pop-

Luckly I then sumbled upon the shinyWidget package and my day immediately improved 10x. shinyWidget offers plenty of stylish and highly customizable input elements to be added to your shiny app directly from R without having to deal with custom CSSs.
I ended up using the airdatePicker element to add an in-line (yes that's right no more annying reactive-unfriendly poup-up calendars)
and used the awesome button from xxxxx that comes from actnButton().



#Back-end: 

The back-end of a ShinyApp is the R code that runs in the background when the user interacts with the input elements of your app. Ideally th
The

My app is not very data-sciency, no questions about that. It could have been much more efficienlty written with some other web-oriented languagage without the need to bring R into it. 
But it's also true that you should simply use whatever language you know/are most comfortable with, and for me, it happens to be R so **shruggy**

As mentioned before, this app doens't relay on R do to some heavy-weight computational-intensive data-science work. in fact. this app doesn't *need* to use R at all and essentially was made more as an excercise/learning experience than anthing else. 

Nontheless, some R code was acutally written for the server side of the app and what it does is querying the setlist.fm API with a GET request and returns a brunch of info about a single All Time Low concert from the useer selected date (if there was one).

The httr package makes it very easy to bring external data from the outside into R and the setlist.fm API offers quite a lot of endpoints to chose from. Since I was only interested in getting data from a single concert the setlist endpoint was perfect for the task. 


The whole block of code above was then placed inside an eventReactive function and linked to the action button below the calendar. WHat this does is delaying the execution of the code until the GO button is clicked. THis also mean that there is no reaction associated with the calendar itself, and nothing happens on the server once the user has selected the date. 

Since the output for this app is simply some new text and a tweet button to show at the bottom of the page, the renderUI/UIoutput functions worked out just fine.





** I actually never took the first introductorty course on Data Reproducibility and gitHub but went straight to the R Programming. A bit ironic considering im writing this post in R Markdown and the source code for the Shiny App is 


** Fun fact: the background photo I used was (by Luna Perri ) is from  the Milan ATL show in April 2017 and I was actually there. 
http://www.recovery-magazine.com/2017/04/13/report-time-low-live-alcatraz-milano-10042017/


```{r cars}
1-1
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=T}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
